Analysis

### 2022-06-11 code/R/Analysis.Rmd
Added second version of onset vs length plot

ggsave("U:/BITCue/Projekter/TrackingFlowers/figures/OnsetVSLength.png", f1, width = 15, height = 10)

all %>% 
ggplot()+
  geom_point(aes(x = flower_start, y = flower_length, colour = CameraID))# +
#geom_smooth(aes(x = flower_start, y = flower_length), method=lm)

t.test(nyaa04_meta$flower_length, nars13_meta$flower_length)

>>>>

#ggsave("U:/BITCue/Projekter/TrackingFlowers/figures/OnsetVSLength.png", f1, width = 15, height = 10)

f2 = all %>% 
ggplot()+
  geom_boxplot(aes(x = flower_start, y = flower_length, fill = camCode, shape = camCode), size = 1) + 
  xlab("Onset of flowering (DOY)") + 
  ylab("Number of days flowering") +
    theme_bw()  +
  scale_fill_manual(name = "Camera ID",
                      values = c("gray26", "brown3", "dodgerblue3", "darkorange2", "chartreuse3"), aesthetics = c("colour", "fill")) + 
  scale_shape_manual(name = "Camera ID",
                      values = c(21,22,23,24,25)) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.title = element_text(size = legendTitleSize),
        text = element_text(size = axisSize),
        legend.text = element_text(size = legendTextSize),
        axis.line = element_line(),
        axis.text=element_text(colour="black"),
        panel.spacing = unit(0.7, "lines"))

ggsave("U:/BITCue/Projekter/TrackingFlowers/figures/OnsetVSLengthBox.png", f2, width = 15, height = 10)

# all %>% 
# ggplot()+
#   geom_point(aes(x = flower_start, y = flower_length, colour = CameraID))# +
# #geom_smooth(aes(x = flower_start, y = flower_length), method=lm)
#  
# t.test(nyaa04_meta$flower_length, nars13_meta$flower_length)
